---
title: "Public Trust and Urban Local Governance"
subtitle: "Evidence from Delhi, India"
author: "Shagun Gupta"
institute: "American University"
date: "April 6, 2023"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(patchwork)
library(survey)

knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, prompt = FALSE,
  tidy = FALSE, comment = NA,
  message = FALSE, warning = FALSE
)

#load IHDS-II survey data set - I downloaded TSV file from the ICPSR repository.
pilot = read_xlsx("pilotdata_DEL2022v1.xlsx")
```

# Data

## Trust in the Municipal Corporation of Delhi (MCD): Pilot Dataset 2022

- Original cross-sectional sample of households in Southeast Delhi.  

- 264 households across 8 unauthorized colonies living under jurisdiction of the South Delhi Municipal Corporation. 

- Conducted in July 2022 as a pilot project for my dissertation. 

- First such data set to analyze trust in local institutions, specifically among residents living in conditions of urban informality in the city. 

---

# Trust in the MCD 

```{r slide one, fig.height=6, fig.width=12, dev='svg'}
#bar plot - all obs. 
pilot %>%
  filter(trustscale != 0) %>%
  group_by(trustscale) %>%
  summarize(
    n = n()) %>%
    mutate(freq = n / sum(n) * 100) %>%
  ggplot(aes(x = trustscale, y = freq, fill = trustscale)) +
  geom_col() +  
  scale_x_discrete(limits = c("1","2","3","4","5"), 
                   breaks = c(1,2,3,4,5),
                   labels=c("Distrust it greatly", 
                            "Tend to distrust it", 
                            "Not sure/don't know", 
                            "Tend to trust it", 
                            "Trust it a great deal")) +
  geom_text(aes(label=round(freq, digits=2)), 
                position=position_dodge(width=0.9), 
                vjust=-0.25, size=5) +
  labs(
    x = "Trust in the MCD", 
    y = "No. of households (% rel. frequency)",
    title = "Trust in the Municipal Corporation of Delhi (N = 246 HHs)")+
  scale_fill_viridis_c() +
  theme_minimal() +                         
  theme(legend.position="none",
        axis.text=element_text(size=10))
```

---

# Neighborhood Associations and Trust

```{r slide two, fig.height=6, fig.width=12, dev='svg'}
#plots - trust by existence of RWAs
plotrwa_yes = pilot %>%
  filter(trustscale != 0, rwa == "Yes") %>%
  group_by(trustscale) %>%
  summarize(
    n = n()) %>%
    mutate(freq = n / sum(n) * 100) %>%
  ggplot(aes(x = trustscale, y = freq, fill = trustscale)) +
  geom_col() +
  scale_x_discrete(limits = c("1","2","3","4","5"), 
                   breaks = c(1,2,3,4,5),
                   labels=c("Distrust it greatly", 
                            "Tend to distrust it", 
                            "Not sure/don't know", 
                            "Tend to trust it", 
                            "Trust it a great deal")) +
  geom_text(aes(label=round(freq, digits=2)), 
                position=position_dodge(width=0.9), 
                vjust=-0.25, size=5) +
  labs(
    x = "Trust in the MCD", 
    y = "No. of households (% rel. frequency)",
    title = "HHs living in colonies WITH RWA/Samiti (N=61)") +
  scale_fill_continuous() +
  theme_minimal() +                         
  theme(legend.position="none",
        axis.text.x=element_text(size=10, angle = 45, hjust = 0.8))

plotrwa_no = pilot %>%
  filter(trustscale != 0, rwa == "No") %>%
  group_by(trustscale) %>%
  summarize(
    n = n()) %>%
    mutate(freq = n / sum(n) * 100) %>%
  ggplot(aes(x = trustscale, y = freq, fill = trustscale)) +
  geom_col() +
  scale_x_discrete(limits = c("1","2","3","4","5"), 
                   breaks = c(1,2,3,4,5),
                   labels=c("Distrust it greatly", 
                            "Tend to distrust it", 
                            "Not sure/don't know", 
                            "Tend to trust it", 
                            "Trust it a great deal")) +
  geom_text(aes(label=round(freq, digits=2)), 
                position=position_dodge(width=0.9), 
                vjust=-0.25, size=5) +
  labs(
    x = "Trust in the MCD", 
    y = "No. of households (% rel. frequency)",
    title = "HHs living in colonies W/O RWA/Samiti (N=142)") +
  scale_fill_continuous() +
  theme_minimal() +                         
  theme(legend.position="none", 
        axis.text.x=element_text(size=10, angle = 45, hjust = 0.8))


plotrwa_yes + plotrwa_no + 
  plot_layout(guides = 'collect', ncol = 2)
```

